---
title: "Lab 7"
author: "Brad McNeney"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message=FALSE)
```

```{r}
library(tidyverse)
library(stringr)
library(ggplot2)
```

## Graphing youth unemployment data

1. Read the youth unemployment data in the file
`API_ILO_country_YU.csv` in the `labs` folder of GitHub
into a data frame called `youthUI`. 
```{r}
youthUI <- read_csv("API_ILO_country_YU.csv")
youthUI
```

2. Reshape the data on different years into key-value pairs 
with key `year` and value `Unemployment Rate`. Convert the 
`year` column to numeric.
```{r}
youthUI <-youthUI %>%
  gather(`2010`:`2014`, key = year, value = `Unemployment Rate`, na.rm = TRUE, convert = TRUE) %>%
  mutate(year = as.numeric(year)) 
youthUI
youthUI %>% 
  summarise(sd(year))


```

3. Plot unemployment rates by year 
for each "country" in `youthUI`. Represent each time series
by a line. Use an appropriate alpha level to manage overplotting.
```{r}
youthUI %>%
  ggplot() + geom_line(mapping = aes(x = year, y = `Unemployment Rate`, group = `Country Name`, alpha = 0.01))
```

4. Using a **regular expression**, extract the subset 
of "Countries" whose `Country.Name` contains the string
"(IDA & IBRD countries)", and save in a data frame
`youthDevel`. (No cheating by using `fixed()`. 
Hint: `(` is a special character string,
so a character string representation of a regexp 
involving `(` would include `"\\(".) Using a **regular expression**,
remove the "(IDA * IBRD countries)" from the country names.
Notes: IDA stands for International Development Association.
Countries that qualify for IDA loans are considered among
the poorest developing countries in the world. 
IBRD stands for International Bank
for Reconstruction and Developent. IBRD countries are considered
middle-income developing countries.
```{r}
youthDevel <- youthUI %>%
  filter(str_detect(`Country Name`,"\\(IDA & IBRD.*\\)"))
youthDevel
```

5. Plot unemployment rates by year 
for each region in `youthDevel` with different colors for each region. 
Your plot should include both points and lines for each region.
Then add a layer that plots the world-wide unemployment data 
from `youthUI` (`Country.Name==World`).
```{r}

world <- filter(youthUI, `Country Name`=="World")
ggplot(mapping = aes(x = year, y = `Unemployment Rate`, group = `Country Name`, alpha = 0.01, color = `Country Name`)) + 
  geom_line(data = youthDevel) + 
  geom_point(data = youthDevel)+
  geom_point(data=world)+
  geom_line(data=world)
```




