---
title: "Lab 8"
author: "Brad McNeney"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message=FALSE)
```

```{r}
library(tidyverse)
library(forcats)
library(lubridate)
yvr <- read_csv("weatherYVR.csv")
yvr
```

In the above code chunk you read in **daily** weather
data from YVR in 2003.

1. Coerce the `Date/Time` variable to a date object
and rename it Date.
```{r}
lab <- yvr %>%
  mutate(`Date/Time` = ymd(`Date/Time`, tz = "America/Vancouver")) %>% 
  rename(Date = `Date/Time`)
lab
```

2. Do a time series plot (with lines) 
of the daily maximum temperature by day.
```{r}
lab %>% 
  ggplot(mapping = aes(x = Date, y = `Max Temp`)) + 
  geom_line()
```

3. Change the `Month` variable from 
numeric to a factor.
(Hint: The `month()` function with the `label=TRUE` will
extract the months from a date-time object.)
```{r}
lab <- lab %>% 
  mutate(Month = month(Date, label = TRUE))
lab
```

4. Plot the average maximum temperature *versus* month,.
Redo this plot with months ordered by 
average maximum.
```{r}
lab %>% 
  group_by(Month) %>%
  summarise(mean = mean(`Max Temp`)) %>%
  ggplot(mapping = aes(x = Month, y = `mean`)) + 
  geom_point()
```
```{r}
lab %>% 
  group_by(Month) %>%
  summarise(mean = mean(`Max Temp`)) %>%
  ggplot(mapping = aes(x = fct_reorder(Month, mean), y = mean)) + geom_point()
```
